%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD in Bioinformatic} % Degree
    {\href{https://www.umontpellier.fr/en/}{University of Montpellier}} % Institution
    {Montpellier, France} % Location
    {Oct. 2017 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Subject: La diversité génétique virale : quel est son rôle dans l'interaction du virus Ostreid herpesvirus 1 et son hôte l’huître Crassostrea gigas ?}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master 2 in Immunology} % Degree
    {\href{https://u-paris.fr/en/universite-de-paris/}{Université de Paris}} % Institution
    {Paris, France} % Location
    {Sep. 2016 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Specialization in Advanced Immunology and Immunopathologies.}
        \item {Advanced Immunology course at Pasteur institute.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master 1 in  Molecular and Cell Biology} % Degree
    {\href{https://u-paris.fr/en/universite-de-paris/}{Université de Paris}} % Institution
    {Paris, France} % Location
    {Sep. 2015 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Specialization in Immunology Fundamental, Immune-pathophysiology, Inflammation and Molecular pathology.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {B.S. in Biochemistry Bioinformatics Biology} % Degree
    {\href{https://u-paris.fr/en/universite-de-paris/}{Université de Paris}} % Institution
    {Paris, France} % Location
    {Sep. 2014 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Specialization in Virology and Chemistry.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {University degree in technology} % Degree
    {\href{http://www.univ-tln.fr/}{University of Toulon}} % Institution
    {Toulon, France} % Location
    {Sep. 2012 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Option biological analysis and biochemistry.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
