%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
 \cventry
    {Biocomputer Scientist} % Job title
    {\href{https://www.sanofi.com/en}{Sanofi}} % Organization
    {Lyon, France} % Location
    {since Jan. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Production of bioinformatics analysis pipelines}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Bioinformatics consultant - specialized in genomics} % Job title
    {\href{https://www.ividata.com/}{IVIDATA Life science}} % Organization
    {Lyon, France} % Location
    {Jul. 2021 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Consultant in bioinformatics for Sanofi: Intervention in VCDS department (microbiology, biochemistry and immunology platform)}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {PhD Student}% Job title
    {\href{http://ihpe.univ-perp.fr/}{University of Montpellier - Host-Pathogen-Environment Interactions}, UMR-5244} % Organization
    {Montpellier, France} % Location
    {Oct. 2017 - Aor. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{https://www.theses.fr/2021MONTG012}{What is the role of viral genetic diversity in the interaction of ostreid herpesvirus 1 and its host, the oyster crassostrea gigas?}}
        \item {Thesis}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Intern - Master Student}% Job title
    {Cochin Institute - \href{https://www.institutcochin.fr/departments/3i/team-lucas/physiology-of-regulatory-foxp3-cd4-t-cells}{Physiology of regulatory Foxp3+ CD4 T cells}, U1016} % Organization Internship
    {Paris, France} % Location
    {Jan. 2017 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Regulation of effector functions of T lymphocytes: From basic research to cancer.}
        \item {Master thesis}
      \end{cvitems}
    }

%


%---------------------------------------------------------
  \cventry
    {Intern - Master student} % Job title
    {Pasteur Institute - LabEx Milieu Interieur} % Organization
    {Paris, France} % Location
    {Nov. 2016 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Characterization of the Immunological situation of healthy individuals using cutting edge technology.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern - Bachelor Student} % Job title
    {Saint Louis hospital - Génétique des virus et Pathogénèse des Maladies Virales, UMR-941} % Organization
    {Paris, France} % Location
    {Apr. 2014 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Inhibition of TNPO3 importin expression in HeLa cells by RNA interference}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Biological analysis technician} % Job title
    {Eurofins Biomnis} % Organization
    {Ivry-sur-Seine, France} % Location
    {Jun. 2015 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Carry out serological analysis on human samples}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
