%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{http://ihpe.univ-perp.fr/}{Host-Pathogen-Environment Interactions}, UMR-5244 - PhD student} % Job title
    {\href{https://doi.org/10.1093/ve/veac039}{Evaluation of tangential flow filtration (TFF) coupled with Oxford Nanopore Technologies (ONT) sequencing for Ostreid herpesvirus type 1 whole-genome reconstruction, Microbial Genomics.}} % Organization
    {University of Montpellier, France} % Location
    {Sep 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Generation of all biological results.}
        %\item Link to article: {\href{https://doi.org/10.1093/ve/veac039}{doi.org/10.1093/ve/veac039}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{http://ihpe.univ-perp.fr/}{Host-Pathogen-Environment Interactions}, UMR-5244 - PhD student} % Job title
    {\href{https://doi.org/10.1093/ve/veac039}{Genetic diversity and connectivity of the Ostreid herpesvirus 1 populations in France: A first attempt to phylogeographic inference for a marine mollusc disease, Virus Evolution.}} % Organization
    {University of Montpellier, France} % Location
    {Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bioinformatics analysis strategy and analysis pipeline writing, implementation of all data visualizations and interpretation of results.}
        \item {First draft of the whole manuscript.}
        \item Link to article: {\href{https://doi.org/10.1093/ve/veac039}{doi.org/10.1093/ve/veac039} and  \href{https://github.com/propan2one/OshV-1-molepidemio}{GitHub code}}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Presenter for <Phylogeography, genetic diversity and connectivity of Ostreid herpesvirus-1 population in France>} % Role
    {\href{https://www.bordeaux-neurocampus.fr/en/event/seminaire-cbib-jean-delmotte/}{Séminaire CBiB (Bordeaux Bioinformatics Center) – Jean Delmotte}} % Event
    {Bordeaux, France} % Location
    {Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Molecular epidemiology to understand viral propagation.}
        \item {Towards a better characterization of phylogenetic relationships using minority variants.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {\href{http://ihpe.univ-perp.fr/}{Host-Pathogen-Environment Interactions}, UMR-5244 - PhD student} % Job title
    {\href{https://doi.org/10.3389/fmicb.2020.01579}{Contribution of Viral Genomic Diversity to Oyster Susceptibility in the Pacific Oyster Mortality Syndrome, Front. Microbiol.}} % Organization
    {University of Montpellier, France} % Location
    {Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bioinformatics analysis by writing the analysis pipeline, implementing all data visualizations and interpretation of results.}
        \item {First draft of the whole manuscript.}
        \item Link to article:  {\href{https://doi.org/10.3389/fmicb.2020.01579}{doi.org/10.3389/fmicb.2020.01579} and  \href{https://github.com/propan2one/DivOsHV-1}{GitHub code}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Presenter for <Characterisation of OsHV-1 µVar genotypic diversity during POMS outbreaks in two French aquaculture area>} % Role
    {\href{https://eafp.org/19-eafp-porto-2019/}{19th International Conference on Diseases of Fish and Shellfish}} % Event
    {Porto, Portugal} % Location
    {Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {History of OsHV-1 genomic diversity.}
        \item {How to evaluate the heterogeneity of viral populations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Presenter for <BibliographeR : a set of tools to help your bibliographic research>  - Text mining} % Role
    {UseR! 2019} % Event
    {Toulouse, France} % Location
    {Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {My first leading project with my friend \href{https://twitter.com/cecilesauder}{Cécile Sauder} !}
        \item {Video of the presentation available at 10:00, \href{https://www.youtube.com/watch?v=6V_nu0K_3mk&list=PL4IzsxWztPdm9_UFnWOCG7Rmw3oW5Fgju}{here}.}
        \item {We performed the presentation as a play !!}
        \\
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
