%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Expertise}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research} % Role
    {Global skills} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Expert innovator: scientific question solving with new approaches, New methods exploration.}
        \item {Scientific writing: Write up experimental results for publication in peer-reviewed journals, Creation of scientific poster.}
        \item {Scientific drawing: Create high quality graphics and logo using vector-based design software (Illustrator/Inkscape).}
        \item {Scientific project: Prepares and writes research projects on small grant applications.}
        \item {Scientific presentation: Popularization of research (Natron / KdenLive).}
        \item {Knowledge management: Keep a bibliographic record up to date (Zotero).}
        \item {Student supervision: tutor of an M2 student (2022).}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Pharmaceutical industry} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Troubleshooting: Genomics investigation, RAE, Assistance in setting up experimental plans.}
        \item {GrP work environment: assistance in writing qualification protocol / qualification report / development report.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Experiment} % Role
    {Biology} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Practical Immunology: Flow cytometry, Cell sorting, Mouse experimentation (lymph nodes removal, orbital blood sample), ELISA.}
        \item {Molecular Biology: DNA extraction, Transfection, ddPCR, qPCR, Western Blot, Cloning, Library preparation, Long reads sequencing}
        \item {Cell culture: Primary cells, HeLA cells, Bacterial culture, Viral culture.}
        \item {Experimental aquaculture: Oyster mortality monitoring, Viral particle filtration and enrichment.}
        \item {Structural biochemistry: SDS-PAGE, Chromatography, Infrared spectroscopy, NMR spectroscopy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fundamental knowledge} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Immunology: Adaptive/innate immune response, T-Cells activation, Cell Ontology, Cancerology, Antiviral response, Host-pathogen interaction.}
        \item {Microbiology: Viral infection, Microbiota Dysbiosis, Holobionte, Pathogenic bacteria, Resistance, Viral evolution, Virus genetic diversity.}
        \item {Evolutionary biology: Evolution theories, Host-pathogen co-evolution, Experimental evolution.}
        \item {Structural biochemistry: CryoEM, 3D crystallisation, FRET, Spectroscopy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Development} % Role
    {Bioinformatics} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {High performance computing clusters: Work on HPC (PBSpro, SLURM).}
        \item {Cloud computing: Amazon Web Services (AWS).}
        \item {Version control: Github/Gitlab.}
        \item {Reproducible analysis: Docker, Singularity, Conda, R-packages, Python envs.}
        \item {Shell scripting: Bash, Powershell.}
        \item {Domaine specific language: Snakemake, Nextflow.}
        \item {R: Tidyverse paradigm, Data mining, Data cleaning, Data visualisation.}
        \item {Data management: Sequencing data management.}
        \item {Management of bioinformatics software: CLCgenomics workbench, Geneious, Ugene, IGV, NGB.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Analysis} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Genomics: Reads mapping, \textit{de novo} genome assembly using long and short reads, Genome annotation, Comparative genomics, Variant calling, Structural variant calling, Genotype reconstruction, Haplotyping and Pangenomics.}
        \item {Phylogenetics: MSA, Inference, Tree Visualisations.}
        \item {Metagenomics: Metabarcoding 16S/18S, Virus discovery, Binning contigs.}
        \item {Transcriptomics: De novo transcriptome assembly, Metatranscriptomics, Differential gene expression, Gene set enrichment analysis.}
        \item {Proteomics: Databases management, Development of a specific peptide library.}
        \item {Structural biology: 3D molecule visualization with pymol, Epitope mapping.}
        \item {Sets analysis: Euclidan sets component dissection, Matrix operations.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}